### 2023-07-26 thesis/sections/4-results.tex
results and discussion

@@

\begin{table}[h]
    \centering
    \begin{tabular}{cccc|ccc|ccc|ccc}
        \toprule
              &         &         &         & \multicolumn{3}{c}{\textbf{Single}} & \multicolumn{3}{c}{\textbf{Dale-2}} & \multicolumn{3}{c}{\textbf{Dale-5}}                                                                                                       \\\cmidrule(lr){5-7}\cmidrule(lr){8-10}\cmidrule(lr){11-13}
        $|V|$ & $h_{s}$ & $h_{r}$ & $e_{s}$ & \textbf{Dist.}                      & \textbf{Acc.}                       & \textbf{length}                     & \textbf{Dist.} & \textbf{Acc.} & \textbf{length} & \textbf{Dist.} & \textbf{Acc.} & \textbf{length} \\\midrule
        {10}  & {10}    & {10}    & {1024}  & {}                                  & {\%}                                & {}                                  & {34,8}         & {24,3\%}      & {1}             & {}             & {\%}          & {}              \\
        {10}  & {10}    & {10}    & {512}   & {}                                  & {\%}                                & {}                                  & {36,3}         & {19,9\%}      & {1
        ,7}   & {}      & {\%}    & {}                                                                                                                                                                                                                              \\
        {13}  & {10}    & {10}    & {1024}  & {}                                  & {\%}                                & {}                                  & {36,3}         & {20,2\%}      & {1}             & {}             & {\%}          & {}              \\
        {20}  & {10}    & {10}    & {1024}  & {}                                  & {\%}                                & {}                                  & {37,8}         & {16,1\%}      & {2}             & {}             & {\%}          & {}              \\
        {100} & {10}    & {10}    & {1024}  & {}                                  & {\%}                                & {}                                  & {37,4}         & {20,1\%}      & {2}             & {}             & {\%}          & {}              \\
        {100} & {100}   & {100}   & {1024}  & {}                                  & {\%}                                & {}                                  & {36,5}         & {20,7\%}      & {2}             & {}             & {\%}          & {}              \\
        \bottomrule
    \end{tabular}
    \caption{Results of the masked coordinate predictor: $|V|$ are different vocabulary sizes, $h$ hidden sizes and $e$ embedding sizes.}
    \label{tab:results_masked_predictor_game}
\end{table}

>>>>

The results of the caption generator game are summarized in Table \ref{tab:results_caption_generator_game}.
In general, it can be seen that the agents have much bigger problems, to solve the task together than a single neural network.
The highest accuracy for descriptions, the agents manage to predict correctly is at 24,6\% for images of the 'Dale-2' dataset.
Compared to the (masked) accuracy of the single model with 72\%, the agents predict 47,4\% points less correct descriptions.
A similar worse performance can be seen for the 'Dale-5' dataset.
Here, the agents only manage to produce for 7,8\% of the images correct descriptions, 13,2\% points less than the single neural model.
The same effect can be seen for the word-by-word accuracy, which is much lower than the metric for the single neural model for both datasets.

When looking, how the different variables affect the performance, it can be seen that a bigger vocabulary size tends to help the agents.
This is only visible for the 'Dale-2' dataset.
With constant hidden sizes of 10, the agents score around 22,9\% with only 10 and 13 available symbols.
When this is increased to 20 and respectively 100 symbols, the agents can increase their accuracy to around 24,5\%.
However, the increase is relatively small.
Interestingly, this effect only occurs, when the hidden sizes are small with only 10 dimensions.
As soon as they are increased to 100 dimensions with a vocabulary size of 100 symbols, the accuracy drops to 21\%.

Looking at the 'Dale-5' dataset, the increase is still there, when the vocabulary is increased to 100 symbols.
Nonetheless, the difference is with 0,5\% points even smaller and the reason may be due to other influences, such as the random initialization of the weights of the agents.
This would need to be confirmed int the future.

@@

\begin{table}[h]
    \centering
    \begin{tabular}{cccc|ccc|ccc|ccc}
        \toprule
              &         &          &         & \multicolumn{3}{c}{\textbf{Single}} & \multicolumn{3}{c}{\textbf{Dale-2}} & \multicolumn{3}{c}{\textbf{Dale-5}}                                                                                                       \\\cmidrule(lr){5-7}\cmidrule(lr){8-10}\cmidrule(lr){11-13}
        $|V|$ & $h_{s}$ & $h_{r}$  & $e_{s}$ & \textbf{Dist.}                      & \textbf{Acc.}                       & \textbf{length}                     & \textbf{Dist.} & \textbf{Acc.} & \textbf{length} & \textbf{Dist.} & \textbf{Acc.} & \textbf{length} \\\midrule
        {10}  & {10}    & {10}     & {1024}  & {19,8}                              & {55,1\%}                            & {2}                                 & {34,8}         & {24,3\%}      & {1}             & {44,3}         & {11,8\%}      & {2}             \\
        {10}  & {10}    & {10}     & {512}   & {9,3}                               & {92\%}                              & {2}                                 & {36,3}         & {19,9\%}      & {1
        ,7}   & {45,9}  & {12,7\%} & {2}                                                                                                                                                                                                                             \\
        {13}  & {10}    & {10}     & {1024}  & {7,8}                               & {96,8\%}                            & {2}                                 & {36,3}         & {20,2\%}      & {1}             & {45,4}         & {11,4\%}      & {2}             \\
        {20}  & {10}    & {10}     & {1024}  & {6,6}                               & {98,3\%}                            & {2}                                 & {37,8}         & {16,1\%}      & {2}             & {45,2}         & {11\%}        & {2}             \\
        {100} & {10}    & {10}     & {1024}  & {5,2}                               & {98,5\%}                            & {2}                                 & {37,4}         & {20,1\%}      & {2}             & {43,6}         & {16,7\%}      & {2}             \\
        {100} & {100}   & {100}    & {1024}  & {12,5}                              & {92,1\%}                            & {2}                                 & {36,5}         & {20,7\%}      & {2}             & {44,6}         & {12,7\%}      & {2}             \\
        \bottomrule
    \end{tabular}
    \caption{Results of the masked coordinate predictor: $|V|$ are different vocabulary sizes, $h$ hidden sizes and $e$ embedding sizes.}
    \label{tab:results_masked_predictor_game}
\end{table}
